Combinatorial interpretations of holonomic recurrences

### 2021-07-26 article/main.tex
Define iteration

\begin{definition}
    Section \(T_{i,j}\) is defined as subset of \(L_i\) adding specific set of nodes. We assign \(j\) according to the lexicographical order of lexicographically sorted node types that need 
\end{definition}

\todo{split into classes / subclasses}
\todo{define iteration}
\todo{remind the cheat}

>>>>

\begin{definition}
    Section \(T_{i,j}\) is defined as subset of \(T_i\) adding specific set of nodes. We assign \(j\) according to the lexicographical order of lexicographically sorted node types.
\end{definition}

\begin{definition}
    Part \(T_{i,j,k}\) is defined as single transformation in section \(T_{i,j}\). \(k\) is assigned according to the order of discovering the transformation.
\end{definition}

In order to make interpretation more human readable, we will be using local notation:

\begin{definition}
    In context of \(T_i\), \(k\) is defined as \((n - i)\).
\end{definition}

\begin{definition}
    In context of \(T_i\), \(C_k\) is defined as \(L(n - i)\), ie.\ number of trees transformations from \(T_i\) are working on.
\end{definition}

\begin{definition}
    Section equation \(E_{i, j}\) is an equation defined in context of \(T_i\) that evaluates to a total number of trees that should be generated by transformations from \(T_{i, j}\).
\end{definition}

\begin{definition}
    Section expression \(S_{i, j}\) is pair of section equation and set of kinds of nodes the transformation introduces.
\end{definition}

For the problem of interpreting trees of lambda terms we define following section expressions:

\[\begin{array}{rccrlc}
        S_{0,0} &=& (& (k + 1) C_k,& \emptyset &)\\
        S_{1,0} &=& (& - (2 k + 1) C_k,& \{l\} &)\\
        S_{1,1} &=& (& - 2 (k + 1) C_k,& \{s\} &)\\
        S_{2,0} &=& (& - (4 k) C_k,& \{aou\} &)\\
        S_{2,1} &=& (& (k) C_k,& \{ll\} &)\\
        S_{2,2} &=& (& (4 k + 2) C_k,& \{ls\} &)\\
        S_{2,3} &=& (& (k + 1) C_k,& \{ss\} &)\\
        S_{3,0} &=& (& 2 (2 k + 1) C_k,& \{aosu\} &)\\
        S_{3,1} &=& (& - (2 k) C_k,& \{lls\} &)\\
        S_{3,2} &=& (& - (2 k + 1) C_k,& \{lss\} &)\\
        S_{4,0} &=& (& k C_k,& \{llss\} &)\\
\end{array}\]

Using context-based variables makes the equation simpler to interpret, as we can immediately see relation between \(k\) and multiplier.

\subsection{Iteration}%
\label{sub:iteration}

As we want to make our work kind of organized, we are going to divide the process into iterations. Each iteration should be a small step into direction of solving the original problem.

We are going to generate two kinds of trees. Positive and negative ones. When computing total number of trees, we count positive tree is counted as \(1\), negative as \(-1\). Our goal is to generate \(E_{i, j}\) trees for each section \(T_{i, j}\).

We start with interpreting \(E_{0,0}\).

\subsection{The cheat}%
\label{sub:the_cheat}

You may ask how we achieved such partial result.
